Interactive Filter and Display of Hillary Clinton's Emails: \\A Cautionary Tale of Metadata

### 2017-04-17 VAST_submission/vgtc_journal_latex/paper.tex
updated the figures to correspond to the varying spoke lengths

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \begin{tabular}{cc}
  \includegraphics[height=0.22\textheight]{EmailSentRecdSept11toNov23} &
  \includegraphics[height=0.22\textheight]{InnerCircleSept11ToNov23} \\
  &\\
  {\small (a) An empty email block: October 30 - November 9} & {\small (b) Inner Circle: Correspondent info by colour; volume by thickness.}
  \end{tabular}
  \caption{Metadata: Time, date, redaction, correspondents, volume, source type.  Filtered: Sept. 11 to Nov. 23, 2012.  
  }

@@

The width of each spoke is proportional to the volume of emails between correspondents.  Whenever the difference in volume is great enough,  correspondents are separated into two groups: those with the greatest correspondence have shorter spokes visually placing them ``closer'' to Clinton.  As \autoref{fig:InnerCircleAll} shows shows, Clinton's closest inner circle are her closest aides Huma Abedin, Cheryl Mills, and Jake Sullivan.
\subsection{Email volume}
\label{sect:Displays:volume}
\autoref{fig:VolumeAll} 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.95\linewidth]{VolumeFullTime}
\caption{Email Volume: All emails (top) ; Those sent by Clinton (bottom)}
\label{fig:VolumeAll}
\end{center}
\end{figure}
presents two time series showing the volume of emails for each day.  In grey at top is the daily total; in magenta at bottom is the total for the subset selected by the filters.  In \autoref{fig:VolumeAll}, the bottom series is the total daily emails that were sent \emph{from} Clinton.

@@

\subsection{The last two years}
We begin our interactive analysis by looking at  email patterns in the last two years of Clinton's tenure as Secretary of State.

\autoref{fig:lastTwoYears} 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.95\linewidth]{EmailVolumeB1LastTwoYears}
\caption{Last two years:  Selected Emails are those that are B1 redacted}
\label{fig:lastTwoYears}
\end{center}
\end{figure}
shows the email volume time series over this period. 
This is accomplished by simply having the right end of the time slider of \autoref{fig:timeSlider} as far right as possible and then moving the left most end towards the middle of the time period until January 1, 2011 is reached.   Note, however, that in addition to filtering on time we have chosen to also filter on FOIA exemption code, selecting only those emails containing one or more B1 (national security and foreign policy matters) redactions.  The magenta time series at the bottom then shows all emails, sent or received by Clinton, in the last two years of her tenure which were redacted in part by the State Department (after the fact, not at the time) as being B1 FOIA exempt.  As can be seen, there are \emph{relatively} few of these.

>>>>

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \begin{tabular}{cc}
  \includegraphics[height=0.2\textheight]{EmailSentRecdSept11toNov23} &
  \includegraphics[height=0.2\textheight]{InnerCircleSept11ToNov23} \\
  &\\
  {\small (a) An empty email block: October 30 - November 9} & {\small (b) Inner Circle: Correspondent info by colour; volume by thickness.}
  \end{tabular}
  \caption{Metadata: Time, date, redaction, correspondents, volume, source type.  Filtered: Sept. 11 to Nov. 23, 2012.  
  }

@@

The width of each spoke is proportional to the volume of emails between correspondents.  
Similarly, the length of each spoke is inversely proportional to the volume of email so 
%Whenever the difference in volume is great enough,  correspondents are separated into two groups: 
those correspondents having the greatest volume will 
%with the greatest correspondence 
have shorter spokes visually placing them ``closer'' to Clinton.  
As \autoref{fig:InnerCircleAll} shows shows, Clinton's closest inner circle are her closest aides Huma Abedin, Cheryl Mills, and Jake Sullivan.
\subsection{Email volume}
\label{sect:Displays:volume}
\autoref{fig:VolumeAll} 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.95\linewidth]{VolumeFullTime}
\caption{Email Volume: All emails (top) ; Those sent by Clinton (bottom)}
\label{fig:VolumeAll}
\end{center}
\end{figure}
presents two time series showing the volume of emails for each day.  In grey at top is the daily total; in magenta at bottom is the total for the subset selected by the filters.  In \autoref{fig:VolumeAll}, the bottom series is the total daily emails that were sent \emph{from} Clinton.

@@

\subsection{The last two years}
We begin our interactive analysis by looking at  email patterns in the last two years of Clinton's tenure as Secretary of State.  
\autoref{fig:lastTwoYears} 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.95\linewidth]{EmailVolumeB1LastTwoYears}
\caption{Last two years:  Selected Emails are those that are B1 redacted}
\label{fig:lastTwoYears}
\end{center}
\end{figure}
shows the email volume time series over this period.

This is accomplished by simply having the right end of the time slider of \autoref{fig:timeSlider} as far right as possible and then moving the left most end towards the middle of the time period until January 1, 2011 is reached.   Note, however, that in addition to filtering on time we have chosen to also filter on FOIA exemption code, selecting only those emails containing one or more B1 (national security and foreign policy matters) redactions.  The magenta time series at the bottom then shows all emails, sent or received by Clinton, in the last two years of her tenure which were redacted in part by the State Department (after the fact, not at the time) as being B1 FOIA exempt.  As can be seen, there are \emph{relatively} few of these.
